Calendar Heatmaps

### 2016-07-27 ab_tests/frequentist_ab_test.Rmd
calendar heatmap
frequentist stats

Select the appropriate test statistic and calculate its value from the data (we will call it ZZ). A test statistic is a single metric that can be used to evaluate the null hypothesis. For our test the underlying metric is a binary yes/no variable (event), which means that the appropriate test statistic is a test for differences in proportions. Math formula:

@@

```{r, message=FALSE, warning=FALSE}
library(scales)
library(ggplot2)
library(data.table)

@@

The shaded dark blue area denotes the significance region, while the the shaded blue area denotes the power. Note that if we pick a smaller N, or a smaller probability difference between the control and experiment group, the power drops (the shaded blue area decreases), meaning that if there’s is in fact a change, there’s lesser percent chance that we’ll detect it:

@@

baseline  <- 0.1  # baseline conversion rate 
delta 	  <- 0.02 # minimum detectable boundary (practical significance boundary)
power 	  <- 0.8  # sensitivity 
sig_level <- 0.05 # specificity

@@

# parameters
baseline  <- 0.1
delta 	  <- 0.02
power 	  <- 0.8
sig_level <- 0.05

result <- power.prop.test( p1 = baseline, p2 = baseline + delta, 
				 		   power = power, sig.level = sig_level,
				 		   alternative = "two.sided" )
result

@@

Suppose you have run the test and you've obtain the total number of sample sizes and the total number of successes for both groups. Given these variables we can use it to calculate whether the proportional change was due to variation or not. To do so, we'll calculate the confidence interval for the difference, which can be done by calculating the difference plus and minus the z score times the standard deviation. Math Formula:

$$p_{experiment} - p_{control} \pm Z \sqrt{ p_{pooled}( 1-p_{pooled} )( \frac{1}{n_{experiment}} + \frac{1}{n_{control}} ) }$$

Note that this is the same formula from the first section, except now we're looking at the confidence interval.

[`ABTest`][ABTest] Function that calculates the confidence interval. Input parameters:

- `count_control` The number of successes. This is equivalent to the number of people that clicked the button for the control group (your original feature).
- `sizes_control` The total number of sample size for the control group.
- The same notion can be applied to the experiment's variable `count_experiment` and `sizes_experiment`.
- Returns : A data.frame consisted of the mean and the confidence interval of the result.

@@

ABTest <- function( count_control = count_control, 
					sizes_control = sizes_control,
					count_experiment = count_experiment, 
					sizes_experiment = sizes_experiment )
{
	# probability of each group 
	p_control <- count_control / sizes_control
	p_experiment <- count_experiment / sizes_experiment

	# p: pooled probability
	# std_error: pooled standard deviation (error) 
	p <- ( count_control + count_experiment ) / ( sizes_experiment + sizes_control )
	std_error <- sqrt( p * ( 1 - p ) * ( 1 / sizes_control + 1 / sizes_experiment ) )

	# 95 percent confidence interval's z score = 1.96, equivalent to qnorm(0.975)
	difference <- p_experiment - p_control
	confidence <- difference + c( -1, 1 ) * qnorm(0.975) * std_error

	return( data.frame( lower = confidence[1], 
						mean  = difference,
						upper = confidence[2] ) )
}

confidence <- ABTest( count_control = count_control, 
					  sizes_control = sizes_control,
					  count_experiment = count_experiment, 
					  sizes_experiment = sizes_experiment )
confidence

@@

```{r, warning=FALSE,message=FALSE}

# fixed artifical plot
# using delta = 0.02 as the minimum detectable boundary 
library(ggplot2)

scenario <- as.character(2:6)
lower <- c( -0.008, 0.011, -0.025, -0.005, 0.015 )
mean  <- c( 0.005, 0.014, 0.005, 0.025, 0.025 )
upper <- c( 0.018, 0.017, 0.035, 0.055, 0.035 )

examples <- data.frame( scenario, lower, mean, upper )
examples <- rbind( cbind( scenario = "1", confidence ), examples )
examples$scenario <- factor( examples$scenario, levels = as.character(6:1) )

@@

[ABTest]: https://github.com/ethen8181/Business-Analytics/blob/master/ab_tests/frequentist_ab_test.R

>>>>

Select the appropriate test statistic and calculate its value from the data (we will call it Z). A test statistic is a single metric that can be used to evaluate the null hypothesis. For our test the underlying metric is a binary yes/no variable (event), which means that the appropriate test statistic is a test for differences in proportions. Math formula:

@@

library(scales)
library(ggplot2)
library(data.table)

@@

The shaded dark blue area denotes the significance region, while the the shaded blue area denotes the power (note that it includes the shaded dark blue area). Note that if we pick a smaller N, or a smaller probability difference between the control and experiment group, the power drops (the shaded blue area decreases), meaning that if there’s is in fact a change, there’s lesser percent chance that we’ll detect it:

@@

baseline  <- 0.1  # baseline conversion rate 
delta 	  <- 0.02 # minimum detectable boundary (practical significance boundary)
power 	  <- 0.8  # specificity, or true negative rate
sig_level <- 0.05 # false positive rate

@@

# parameters
baseline  <- 0.1
delta 	  <- 0.02
power 	  <- 0.8
sig_level <- 0.05
result <- power.prop.test( p1 = baseline, p2 = baseline + delta, 
				 		   power = power, sig.level = sig_level,
				 		   alternative = "two.sided" )
result

@@

Suppose you have run the test and you've obtain the total number of sample sizes and the total number of successes for both groups. Given these variables we can use it to calculate whether the proportional change was due to variation or not.

- `count_control` The number of successes. This is equivalent to the number of people that clicked the button for the control group (your original feature).
- `sizes_control` The total number of sample size for the control group.
- The same notion can be applied to the experiment's variable `count_experiment` and `sizes_experiment`.

@@

result <- prop.test( c( count_control, count_experiment ), 
					 c( sizes_control, sizes_experiment ) )
result

# do the computation ourselves to see that the confidence interval matches
# compute the probability of each group and the standard error
p1 <- count_control / sizes_control
p2 <- count_experiment / sizes_experiment
se <- sqrt( p1 * ( 1 - p1 ) / sizes_control + p2 * ( 1 - p2 ) / sizes_experiment )

# 95 percent confidence interval's z score
conf_level <- 0.95
zscore <- qnorm( conf_level + ( 1 - conf_level ) / 2 )
conf_int <- abs(p2 - p1) + c( -1, 1 ) * zscore * se
conf_int

@@

```{r, warning=FALSE, message=FALSE}

scenario <- as.character(1:6)
lower <- c( conf_int[1], -0.008, 0.011, -0.025, -0.005, 0.015 )
mean  <- c( abs(p2 - p1), 0.005, 0.014, 0.005, 0.025, 0.025 )
upper <- c( conf_int[2], 0.018, 0.017, 0.035, 0.055, 0.035 )
examples <- data.frame( scenario, lower, mean, upper )
examples$scenario <- factor( examples$scenario, levels = as.character(6:1) )

@@

### 2016-07-27 articles/articles.Rmd
frequentist stats

<style type="text/css">
p{ /* Normal  */
   font-size: 18px;
}
body{ /* Normal  */
   font-size: 18px;
}
td {  /* Table  */
   font-size: 14px;
}
h1 { /* Header 1 */
 font-size: 32px;
}
h2 { /* Header 2 */
 font-size: 26px;
}
h3 { /* Header 3 */
 font-size: 22px;
}
code.r{ /* Code block */
  font-size: 14px;
}
pre { /* Code block */
  font-size: 14px
}
</style>

@@

- The Single Most Important Skill for a Data Scientist. [[Mango Solution](http://www.mango-solutions.com/wp/2015/06/the-single-most-important-skill-for-a-data-scientist/)]
- How A/B Testing at LinkedIn, Wealthfront and eBay Made Me a Better Manager. [[First Round Review](http://firstround.com/review/how-a-b-testing-at-linkedin-wealthfront-and-ebay-made-me-a-better-manager/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
- How Constraints Create Space for Innovation. [[linkedin pulse](https://www.linkedin.com/pulse/how-constraints-create-space-innovation-ash-maurya)]
- From Developer to Manager - PyCon 2016. [[Youtube](https://www.youtube.com/watch?v=lzBm0r8CxhY)]
- Reddit and Facebook Veteran On How to Troubleshoot Troublemakers. [[First Round Review](http://firstround.com/review/reddit-and-facebook-veteran-on-how-to-troubleshoot-troublemakers/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
    - Hermits. Get them to collaborate with a team.
    - Nostalgia. Ask qualities that they missed most, and see if there're existing projects that could allow them to recapture that feeling.
    - Trend Chaser. Ask them why this is the route their going to take? The potential has to worth more than the expense of experimenting.
- Practical Frameworks for Beating Burnout [[First Round Review](http://firstround.com/review/practical-frameworks-for-beating-burnout/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
- How to set goals: OKRs. [[Youtube](https://www.youtube.com/watch?v=mJB83EZtAjc)]
- Meetings that don’t suck. [[Youtube](https://www.youtube.com/watch?v=rU8nv38E0Qk)]

@@

@@

- 'Amazon is not your friend'. [[Linkedin](https://www.linkedin.com/pulse/amazon-your-friend-caroline-fairchild)]
    - The only way to survive is to build a brand that can grow without Amazon’s distribution.
    - Amazon hasn’t proven that it can build inspirational brands. While they have mastered the ability to get customers commodity products, no one goes to Amazon to discover something they didn’t already know about.
- Facebook is the new Excel. [[blog](http://alexmuir.com/facebook-is-the-new-excel)]
- We need companies to start innovating instead of imitating success stories. [[Hustle](http://thehustle.co/snapchat-vs-spacex-battle-of-the-imitators-and-innovators)]
- My 4+ Years At Uber Taught Me These Key Lessons. 1. May the supply be with you ; 2. Don't listen, show them. [[Linkedin](https://www.linkedin.com/pulse/three-things-i-learned-during-4-years-uber-michael-pao)]

@@

- The MBA Data Science Toolkit: 8 resources to go from the spreadsheet to the command line. [[Medium](https://medium.com/@dmca/the-mba-data-science-toolkit-8-resources-to-go-from-the-spreadsheet-to-the-command-line-cbb59ea82144#.pjph91n3m)]

>>>>

<style type="text/css">
p{ /* Normal  */
   font-size: 18px;
}
body{ /* Normal  */
   font-size: 18px;
}
td{  /* Table  */
   font-size: 14px;
}
h1{ /* Header 1 */
 font-size: 32px;
}
h2{ /* Header 2 */
 font-size: 26px;
}
h3{ /* Header 3 */
 font-size: 22px;
}
code.r{ /* Code block */
  font-size: 14px;
}
pre{ /* Code block */
  font-size: 14px
}
</style>

@@

- The Pivotal Stories Every Startup Leader Should Be Able to Tell. [[First Round Review](http://firstround.com/review/the-pivotal-stories-every-startup-leader-should-be-able-to-tell/)]
- The Eisenhower Matrix Productivity Tool – As A Trello Board. [[Trello](http://blog.trello.com/eisenhower-matrix-productivity-tool-trello-board/?utm_source=newsletter&utm_medium=email&utm_campaign=july-2016-newsletter-2)]
- All About OKRs: How to Set Them, Achieve Them, and Track Them in Trello. [[Trello](http://blog.trello.com/okrs-set-achieve-track-trello/?utm_source=newsletter&utm_medium=email&utm_campaign=july-2016-newsletter-2)]
- The Single Most Important Skill for a Data Scientist. [[Mango Solution](http://www.mango-solutions.com/wp/2015/06/the-single-most-important-skill-for-a-data-scientist/)]
- How A/B Testing at LinkedIn, Wealthfront and eBay Made Me a Better Manager. [[First Round Review](http://firstround.com/review/how-a-b-testing-at-linkedin-wealthfront-and-ebay-made-me-a-better-manager/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
- How Constraints Create Space for Innovation. [[linkedin pulse](https://www.linkedin.com/pulse/how-constraints-create-space-innovation-ash-maurya)]
- From Developer to Manager - PyCon 2016. [[Youtube](https://www.youtube.com/watch?v=lzBm0r8CxhY)]
- Reddit and Facebook Veteran On How to Troubleshoot Troublemakers. [[First Round Review](http://firstround.com/review/reddit-and-facebook-veteran-on-how-to-troubleshoot-troublemakers/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
    - Hermits. Get them to collaborate with a team.
    - Nostalgia. Ask qualities that they missed most, and see if there're existing projects that could allow them to recapture that feeling.
    - Trend Chaser. Ask them why this is the route their going to take? The potential has to worth more than the expense of experimenting.
- Practical Frameworks for Beating Burnout [[First Round Review](http://firstround.com/review/practical-frameworks-for-beating-burnout/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
- How to set goals: OKRs. [[Youtube](https://www.youtube.com/watch?v=mJB83EZtAjc)]
- Meetings that don’t suck. [[Youtube](https://www.youtube.com/watch?v=rU8nv38E0Qk)]

@@

- Data science tips from reddit
The Top Five Data Science Tips From r/DataScience. [[Blog](http://www.datadependence.com/2016/07/best-data-science-tips-reddit/?utm_content=buffer076f2&utm_medium=social&utm_source=twitter.com&utm_campaign=buffer)]
- Data scientists mostly just do arithmetic and that’s a good thing. [[Blog](https://m.signalvnoise.com/data-scientists-mostly-just-do-arithmetic-and-that-s-a-good-thing-c6371885f7f6#.dly3ud86c)]
- The one machine learning concept you need to know. [[Blog](http://www.sharpsightlabs.com/one-concept-machine-learning/)]
    - When you’re doing machine learning (specifically, supervised learning), you’re essentially using computational techniques to find the underlying relationships between the input and the output.

@@

- The New 'Must Haves' for Mobile Apps to Succeed Today. [[First Round Review](http://firstround.com/review/the-new-must-haves-for-mobile-apps-to-succeed-today/)]
- 'Amazon is not your friend'. [[Linkedin](https://www.linkedin.com/pulse/amazon-your-friend-caroline-fairchild)]
    - The only way to survive is to build a brand that can grow without Amazon’s distribution.
    - Amazon hasn’t proven that it can build inspirational brands. While they have mastered the ability to get customers commodity products, no one goes to Amazon to discover something they didn’t already know about.
- Facebook is the new Excel. [[blog](http://alexmuir.com/facebook-is-the-new-excel)]
- We need companies to start innovating instead of imitating success stories. [[Hustle](http://thehustle.co/snapchat-vs-spacex-battle-of-the-imitators-and-innovators)]
- My 4+ Years At Uber Taught Me These Key Lessons. 1. May the supply be with you ; 2. Don't listen, show them. [[Linkedin](https://www.linkedin.com/pulse/three-things-i-learned-during-4-years-uber-michael-pao)]

@@

- The Mathematics of Machine Learning. [[Blog]](http://datascience-africa.org/2016/07/mathematics-machine-learning/)
- The MBA Data Science Toolkit: 8 resources to go from the spreadsheet to the command line. [[Medium](https://medium.com/@dmca/the-mba-data-science-toolkit-8-resources-to-go-from-the-spreadsheet-to-the-command-line-cbb59ea82144#.pjph91n3m)]

### 2016-07-27 articles/calendar_heatmaps/calendar_heatmaps.Rmd
frequentist stats

library(DT)
library(dplyr)
library(scales)
library(viridis)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lubridate)
library(data.table)
setwd('/Users/ethen/Business-Analytics/articles/calendar_heatmaps')

attacks <- fread("data/eventlog.csv")
DT::datatable(attacks)

@@

@@

- [Making faceted heatmaps with ggplot2](https://rud.is/b/2016/02/14/making-faceted-heatmaps-with-ggplot2/)

>>>>

library(dplyr)
library(scales)
library(viridis)
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(lubridate)
library(data.table)
setwd('/Users/ethen/Business-Analytics/articles/calendar_heatmaps')

attacks <- fread("data/eventlog.csv")
head(attacks)

@@

This type of calendar heatmap can also be used to detect patterns in IT support logs, the chart will then show the number of tickets raised (day-wise). We can then detect patterns to see commonly raised issues and figure out ways to address it.

@@

- [Making faceted heatmaps with ggplot2](https://rud.is/b/2016/02/14/making-faceted-heatmaps-with-ggplot2/)
- [Big Data Insights - IT Support Log Analysis](http://costaleconomist.blogspot.tw/2015/12/big-data-insights-it-support-log.html)
